Fourmile_inputs

### 2022-10-09 fourmile_inputs.Rmd
got precip prism shift for cals, moved runoff ratios to data process Rmd

>>>>

#####################################################################
#get prism shift only for precip (for year round)
prec_orig <- read_csv('precipAll.csv')

prec_prismshift <- prec_orig %>%
  dplyr::select(c(date, prism_W, prism_M, prism_E)) %>%
  mutate(date = dmy(date)) %>%
  mutate(prism_most_w = prism_W * 0.974,
         prism_little_w = prism_W * 0.026,
         prism_most_m = prism_M * 0.974,
         prism_little_m = prism_M * 0.026,
         prism_most_e = prism_E * 0.974,
         prism_little_e = prism_E * 0.026) %>%
  mutate_at(c('prism_most_w', 'prism_most_m', 'prism_most_e'), list(lead), n = 1) %>%
  mutate(prism_W = prism_most_w + prism_little_w,
         prism_M = prism_most_m + prism_little_m,
         prism_E = prism_most_e + prism_little_e) %>%
  dplyr::select(-c(prism_most_w, prism_little_w,
                   prism_most_m, prism_little_m,
                   prism_most_e, prism_little_e)) %>%
  filter(date > '2009-12-31') %>%
  mutate(date = format(as.Date(date), '%d.%m.%Y'))

write.csv(prec_prismshift, 'precip_prismshift.csv')
#####################################################
